Highly Available Transactions: Virtues and Limitations

### 2013-04-01 writeup/futurework.tex
fixed

\textbf{Where do semantics-based concurrency control and weakened
  failure models lie in the HAT landscape?} The vast
literature on semantics-based concurrency control provides hints as to
when coordination can be avoided while providing ``strongly
consistent'' outcomes for limited failure scenarios. We have performed
a narrow case study in this work, but a general taxonomization of
techniques such as escrow transactions~\cite{escrow},
Sagas~\cite{sagas}, and other long-running transaction support could
help answer the challenge of programming in a weakly consistent
environment. HAT guarantees can also be strengthened by considering
weaker failure models such as bounded asynchrony or models in which
the underlying hardware provides explicit service-level
agreements. Additionally, while we have focused on systems that
provide a single availability mode, there are several interesting
hybrids to consider. For example, a system may provide ``best-effort''
stickiness (or serializability) in the absence of partitions, but, in
the presence of partitions, ``lose'' guarantees by having clients
reconnect to an available replica. This strategy provides stronger
guarantees in the absence of partitions but, to provide availability,
sacrifices them in the event of partitions.

>>>>

\textbf{Where do semantics-based concurrency control and weakened
  failure models lie in the HAT landscape?} The vast
literature on semantics-based concurrency control indicates 
when coordination can be avoided while providing ``strongly
consistent'' outcomes for limited failure scenarios. We have performed
a narrow case study in this work, but a general taxonomization of
techniques such as escrow transactions~\cite{escrow},
Sagas~\cite{sagas}, and other long-running transaction support could
help answer the challenge of programming in a weakly consistent
environment. HAT guarantees can also be strengthened by considering
weaker failure models such as bounded asynchrony or models in which
the underlying hardware provides explicit service-level
agreements. Additionally, while we have focused on systems that
provide a single availability mode, there are several interesting
hybrids to consider. For example, a system may provide ``best-effort''
stickiness (or serializability) in the absence of partitions, but, in
the presence of partitions, ``lose'' guarantees by having clients
reconnect to an available replica. This strategy provides stronger
guarantees in the absence of partitions but, to provide availability,
sacrifices them in the event of partitions.
